\Large \bf Direct-style process creation on Linux

### 2020-05-28 research/paper/paper.tex
paper......

\begin{document}
\newcommand{\twosigma}{{[tech company]}}
\newcommand{\githuburl}{[Github url removed]}
\date{}
\title{\Large \bf DRAFT: Direct-style process creation on Linux}
% \author{
% {\rm Spencer Baugh}\\
% Two Sigma
% }
\maketitle
\begin{abstract}
Traditional process creation interfaces,
such as \texttt{fork} and \texttt{spawn},
are complex to use, limited in power, and difficult to abstract over.
We develop a new process creation interface for Linux
which allows a program to create a child process in a non-running state
and initialize the new process by operating on it from the outside.
This method of process creation results in more comprehensible programs, 
has better error handling,
is comparably efficient,
and is more amenable to abstraction.
Our implementation is immediately deployable without kernel modifications on any recent Linux kernel version.
\end{abstract}

@@

\texttt{rsyscall} can be conceptually divided in two parts:
the basic syscall primitive,
and a language-specific library built on top.
The Python language-specific library has already been demonstrated above.
Such libraries only need to be able to call syscalls and explicitly specify a process in some way;
they are, for the most part, agnostic to how the syscall primitive is implemented.
The syscall primitive takes a syscall number, and some number of register-sized integer arguments,
and arranges to call that syscall in the specified process,
returning the response as a single register-sized integer.

@@

When making a syscall in another process,
\texttt{rsyscall}'s default userspace cross-process syscall primitive sends the syscall request
to a userspace ``syscall server'' running in the target process,
which performs the syscall and sends the response back.
Communication to the syscall server happens over file descriptors,
typically a pair of pipes.
The syscall server runs on the main and only thread of the target process,
and is the only userspace code running in an rsyscall-controlled child process;
when not executing a syscall or writing out the response,
an rsyscall-controlled child process spends all its time blocked in \texttt{read},
waiting for new syscall requests.

@@

\texttt{ptrace} already provides an in-kernel way to perform arbitrary actions on a target process,
including system calls,
but is not suitable for us\cite{ptrace}.
As we discuss in section \ref{related}, a number of systems, such as \texttt{gdb} and \texttt{strace},
use \texttt{ptrace} to implement debuggers.
But multiple processes cannot use \texttt{ptrace} on a single target process at the same time;
thus, if we used \texttt{ptrace} to implement \texttt{rsyscall},
such debugging tools would not work on \texttt{rsyscall}-controlled processes,
which is an unacceptable limitation for a general-purpose utility.

>>>>

\begin{document}
\newcommand{\twosigma}{{[tech company]}}
\newcommand{\githuburl}{[Github url removed]}
\date{}
\title{\Large \bf Direct-style process creation on Linux}
% \author{
% {\rm Spencer Baugh}\\
% Two Sigma
% }
\maketitle
\begin{abstract}
Traditional process creation interfaces,
such as \texttt{fork} and \texttt{spawn},
are complex to use, limited in power, and difficult to abstract over.
We develop a new process creation interface for Linux
which allows a program to create a child process in a non-running state
and initialize the new process by operating on it from the outside.
This method of process creation results in more comprehensible programs, 
has better error handling,
is comparably efficient,
and is more amenable to abstraction.
Our implementation is immediately deployable without kernel modifications on any recent Linux kernel version.
\end{abstract}

@@

\texttt{rsyscall} can be conceptually divided in two parts:
the basic syscall primitive,
and a language-specific library built on top.
The Python language-specific library has already been demonstrated above.
Such libraries only need to be able to call syscalls and explicitly specify a process in some way;
they are, for the most part, agnostic to how the syscall primitive is implemented.
The syscall primitive takes a syscall number, and some number of register-sized integer arguments,
and arranges to call that syscall in the specified process,
returning the result as a single register-sized integer.

@@

When making a syscall in another process,
\texttt{rsyscall}'s default userspace cross-process syscall primitive sends the syscall request
to a userspace ``syscall server'' running in the target process,
which performs the syscall and sends the result back.
Communication to the syscall server happens over file descriptors,
typically a pair of pipes.
The syscall server runs on the main and only thread of the target process,
and is the only userspace code running in an rsyscall-controlled child process;
when not executing a syscall or writing out the result,
an rsyscall-controlled child process spends all its time blocked in \texttt{read},
waiting for new syscall requests.

@@

\texttt{ptrace}\cite{ptrace} already provides an in-kernel way to perform arbitrary actions on a target process,
including system calls,
but is not suitable for us.
As we discuss in section \ref{related}, a number of systems, such as \texttt{gdb} and \texttt{strace},
use \texttt{ptrace} to implement debuggers.
But multiple processes cannot use \texttt{ptrace} on a single target process at the same time;
thus, if we used \texttt{ptrace} to implement \texttt{rsyscall},
such debugging tools would not work on \texttt{rsyscall}-controlled processes,
which is an unacceptable limitation for a general-purpose utility.
